Google Analytics Visualizations
==========================================

 **Jesus Martin** - *INSEAD MBA 15J*
 
 jesus.martin.calvo@gmail.com
 
 In this report we will show how to create visualizations with data from Google Analytics
 to understand user behavior in a website. If you were able to download the data from your
 Google Analytics account, you will have some insights about how users interact with your
 website. If you are using the example data provided. you will see how users have interacted
 with the website www.encortosabemejor.com. 
 
 
First, let's take a look at the data

```{r, echo=FALSE, message=FALSE, prompt=FALSE, results='asis'}
t1 <- gvisTable(gadata,options=list(showRowNumber=TRUE,width=800, height=min(400,27*(nrow(gadata)+1)),allowHTML=TRUE,page='disable'))
print(t1,'chart')
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
